\def\pilot{{\tt PILOT}}
\def\RR{{\tt SAIL}}
\def\bb{\noindent\hspace{.46cm}$\bullet$\hspace{.19cm}}

\UseRawInputEncoding


\documentclass[10pt]{article}

%\usepackage{simplemargins}
%\setallmargins{1in}

\usepackage{url}
\evensidemargin -.2cm
\oddsidemargin -.2cm
\setlength\topmargin{-0.7in}
\setlength{\textwidth}{16cm}   % width of body
\setlength{\textheight}{9.2in}   % heigth of body
%\setlength{\sectionskip}{2ex}
\setlength{\itemsep}{-1in}
\setlength{\leftmarginii}{.05in}

\newcommand{\ve}[1]{{\em #1}} % venue of publication
\newcommand{\ti}[1]{``#1''} % title of publication
\newcommand{\lmt}{(limited to period starting 01/2013)}

\begin{document}


%\pagestyle{empty}

\begin{center}
{\Large \bf CURRICULUM VITAE\\
\bigskip{\large \bf Mihai Surdeanu}}
\end{center}
\smallskip

  \makebox{
     \parbox{2.6in}{\centering
     {\small
     Department of Computer Science\\
     University of Arizona\\
     Tucson, AZ 85721\\
}
     }
   \nolinebreak
     \parbox{3.2in}{\centering
	{\small
     Web page: \url{www.surdeanu.info/~mihai} \\
     Email: msurdeanu@email.arizona.edu\\
     Phone: (520) 626 -- 2706
	}
  }}
\bigskip

\begin{description}

\item [Education]\

\begin{tabular}{lp{4.5in}}
\hspace{-.2cm}2001 &  Ph.D.~Computer Science, {\sc Southern Methodist University}
\\\vspace{.0cm}&Thesis: Domain Adaptation in Textual Entailment
\\\vspace{.1cm}& Adviser: Dan~Moldovan\\
\vspace{.1cm}\hspace{-.2cm}1997 &  M.S.~Computer Science, {\sc Technical University of Cluj-Napoca} \\
\hspace{-.2cm}1996 & B.S.~Computer Science,  {\sc Technical University of Cluj-Napoca}
\end{tabular}


\item [Professional Experience]\

\begin{tabular}{lp{4.9in}}
\hspace{-.2cm}2015 -- present & Associate Professor\\\vspace{.1cm}
& Computer Science, {\sc University of Arizona}\\\vspace{.1cm}
& Courtesy appointments: Linguistics, Cognitive Science\\

\hspace{-.2cm}2013 -- 2015 & Associate Professor\\\vspace{.1cm}
& SISTA, {\sc University of Arizona} \\

\hspace{-.2cm}2008 -- 2012 & Senior Research Scientist\\\vspace{.1cm}
& Computer Science, {\sc Stanford University} \\

\hspace{-.2cm}2010 -- 2012 & Chief Technology Officer\\\vspace{.1cm}
& {\sc Lex Machina} \\

\hspace{-.2cm}2007 -- 2008 & Senior Research Scientist\\\vspace{.1cm}
& {\sc Yahoo! Research Barcelona/Barcelona Media Innovation Center} \\

\hspace{-.2cm}2004 -- 2007 & Senior Research Scientist\\\vspace{.1cm}
& Computer Science, {\sc Technical University of Catalonia} \\

\hspace{-.2cm}2001 -- 2004 & Vice President of Engineering\\\vspace{.1cm}
& {\sc Language Computer Corp.} \\

\hspace{-.2cm}2000 -- 2001 & Research Scientist\\
& {\sc Language Computer Corp.} 

\end{tabular}

\vspace{-.3cm}
\item [Honors, Awards, and Memberships]\

Recipient of the Faculty Research award, CS, UA, 2017 \\
Led team ranked 1st  at the CoNLL shared task (coreference resolution), 2011 \\
Member of team ranked 1st at the BioNLP shared task (bio-medical event extraction), 2011\\
Member of team ranked 3rd at the CoNLL shared task (semantic and syntactic parsing), 2008\\
Led team ranked 2nd at the ACE evaluation (relation extraction), 2007\\
Member of team ranked 1st at the CLEF shared task, QA on speech transcripts track, 2007\\
``Ramon y Cajal'' grant (similar to the NSF CAREER award in Spain), 2004 \\
Member of team ranked 1st at the TREC evaluation, QA track, 2001\\
Member of team ranked 1st at the TREC evaluation, QA track, 2000 \\
Outstanding graduate student award, Southern Methodist University, 2000 \\
``Frederick E. Terman'' top graduate student award, Southern Methodist University, 1999 \\

\vspace{-.3cm}\item [Department Committee Service]\

Director of graduate affairs committee, Computer Science, 2016 -- 2017\\
Faculty recruiting committee, Computer Science, 2015\\
Executive committee of the School of Information, 2013 -- 2014\\
Advanced studies committee, School of Information, 2013 -- 2014\\
Computing committee, SISTA, 2013 -- 2014\\

\vspace{-.3cm}\item [University Committee Service]\

APR committee for the Linguistics department at University of Arizona, 2017 \\

\vspace{-.3cm}\item [Program Committee Service] \lmt \

Area chair, Empirical Methods for Natural Language Processing (EMNLP), 2017 \\
PC member, Association of Computational Linguistics (ACL), 2013 -- 2017\\
PC member, EVENTS Workshop at ACL, 2013 -- 2017\\
PC member, Empirical Methods for Natural Language Processing (EMNLP), 2013 -- 2016 \\
PC member, International Joint Conference on Artificial Intelligence (IJCAI), 2016\\
PC member, SIGIR Web Question Answering beyond Factoids (WebQA) Workshop, 2016 \\
Area chair, North-American Chapter of the Assoc. for Comp. Linguistics (NAACL), 2016 \\
PC member, North-American Chapter of the Assoc. for Comp. Linguistics (NAACL), 2013 -- 2015\\
PC member, International Conference on Parsing Technologies (IWPT), 2015\\
PC member, SemEval Workshop, 2015 \\
Area chair, Association of Computational Linguistics (ACL), 2014\\
PC member, European Chapter of the Association for Computational Linguistics (EACL), 2014 \\
PC member, Conference on Natural Language Learning (CoNLL), 2013 \\

\vspace{-.4cm}\item [Conference Committee Service] \lmt \

Organizing Committee, NIST Knowledge Base Population (KBP) shared task, 2013 -- 2014\\

\vspace{-.4cm}\item [Steering Committees and Editorial Boards] \lmt \

Editorial Board, Transactions of the Assoc. of Computational Linguistics (TACL), 2013 -- present \\

\vspace{-.4cm}\item [Journal Reviews] \lmt \

Transactions of the Association for Computational Linguistics (TACL)\\
Computational Linguistics (CL)\\
Journal of Artificial Intelligence Research (JAIR)\\
Natural Language Engineering (NLE) \\

\vspace{-.4cm}\item [Proposal Reviews] \lmt \

Army Research Office (ARO) proposal review, 2017 \\
NSF CAREER award proposal review, 2013 \\

\vspace{-.4cm}\item [Book Chapters]\
%(all authors listed in alphabetical order)]\ 

\begin{enumerate}
%\setcounter{enumi}{55}

\item Jordi Turmo, Mihai Surdeanu, Olivier Galibert, Sophie Rosset. Language Technologies: Question Answering in Speech Transcripts. Chapter 8, pp. 75--86, in Computers in the Human Interaction Loop, edited by Alexander Waibel and Rainer Stiefelhagen. Publisher: Springer London, ISBN 978-1-84882-053-1 (Print) and 978-1-84882-054-8 (Online).

\item Dan Moldovan, Marius Pasca, Mihai Surdeanu. Some Advanced Features of LCC's PowerAnswer. Chapter 1, pp. 3--34, in Advances in Open Domain Question Answering, edited by Tomek Strzalkowski and Sanda Harabagiu. Publisher: Springer Netherlands, ISBN 978-1-4020-4744-2 (Print) 978-1-4020-4746-6 (Online)

\end{enumerate}



\item [Peer-Reviewed Journal Publications]\ 

(Publications preceded by * are substantively based on work done as a graduate student)


\begin{enumerate}
\setcounter{enumi}{2}

\item
Heeyoung Lee, Mihai Surdeanu, and Dan Jurafsky.   \ti{A Scaffolding Approach to Coreference Resolution Integrating Statistical and Rule-based Models}. Accepted to \ve{Natural Language Engineering (NLE)}, February 2017.

\item
Peter Jansen, Rebecca Sharp, Mihai Surdeanu, and Peter Clark.  \ti{Framing QA as Creating and Ranking Intersentence Answer Justifications}. Accepted to \ve{Computational Linguistics}, February 2017.

\item
Daniel Fried, Peter Jansen, Gustave Hahn-Powell, Mihai Surdeanu, and Peter Clark.  \ti{Higher-order Lexical Semantic Models for Non-factoid Answer Reranking}. \ve{Transactions of the Association for Computational Linguistics (TACL)}, 3, 2015.

\item
Heeyoung Lee, Angel Chang, Yves Peirsman, Nathanael Chambers, Mihai Surdeanu and Dan Jurafsky.  \ti{Deterministic coreference resolution based on entity-centric, precision-ranked rules}. \ve{Computational Linguistics}, 39(4), 2013.

\item
Benat Zapirain, Eneko Agirre, Lluis Marquez and Mihai Surdeanu.  \ti{Selectional Preferences for Semantic Role Classification}. \ve{Computational Linguistics}, 39(3), 2013.

\item
David McClosky, Sebastian Riedel, Mihai Surdeanu, Andrew McCallum, and Christopher D. Manning.  \ti{Combining Joint Models for Biomedical Event Extraction}. \ve{BMC Bioinformatics}, 13(Suppl 11):S9, 2012.

\item
Mihai Surdeanu, Massimiliano Ciaramita, Hugo Zaragoza.Ê \ti{Learning to Rank Answers to Non-Factoid Questions from Web Collections}. \ve{Computational Linguistics}, 37(2), 2011.

\item
David Dominguez-Sal, Josep Aguilar-Saborit, Mihai Surdeanu, Josep Lluis Larriba-Pey.Ê \ti{Using Evolutive Summary Counters for Efficient Cooperative Caching in Search Engines}.Ê \ve{IEEE Transactions on Parallel and Distributed Systems}, 99, pp. 776--784, 2011.

\item
Pere R. Comas, Jordi Turmo, Mihai Surdeanu.  \ti{Robust Question Answering for Speech Transcripts Using Minimal Syntactic Analysis}. \ve{Lecture Notes in Computer Science: Advances in Multilingual and Multimodal Information Retrieval}, 5152/2008, pp. 424--432, 2008.

\item
Mihai Surdeanu, Llluis Marquez, Xavier Carreras, and Pere R. Comas.  \ti{Combination Strategies for Semantic Role Labeling}. \ve{Journal of Artificial Intelligence Research (JAIR)}, 29, 2007. 

\item
Dan Moldovan, Marius Pasca, Sanda Harabagiu, and Mihai Surdeanu.  \ti{Performance Issues and Error Analysis in an Open-Domain Question Answering System}. \ve{ACM Transactions in Information Systems}, 21(2), pp. 1--22, 2003.

\item
Dan Moldovan and Mihai Surdeanu.  \ti{On the Role of Information Retrieval and Information Extraction on Question Answering Systems}. \ve{Information Extraction in the Web Era}, pp. 129--147, 2003.

\item
[* \addtocounter{enumi}{1}\theenumi ]
Mihai Surdeanu, Dan Moldovan, and Sanda Harabagiu.  \ti{Performance Analysis of a Distributed Question/Answering System}. \ve{IEEE Transactions on Parallel and Distributed Systems}, 13(6), pp. 579--597, 2002. 

\item
[* \addtocounter{enumi}{1}\theenumi ]
Mihai Surdeanu and Dan Moldovan.  \ti{Design and Performance Analysis of a Distributed Java Virtual Machine}. \ve{IEEE Transactions on Parallel and Distributed Systems}, 13(6), pp. 611--628, 2002.

\end{enumerate}

\item [Competitive Peer-Reviewed Conference Publications]\

(Publications preceded by * are substantively based on work done as a graduate student. Citation statistics were obtained from this website: {\small \url{https://aminer.org/conferencebestpapers}})

\begin{enumerate}
\setcounter{enumi}{16}

\item
Gustave Hahn-Powell, Marco A. Valenzuela-Escarcega, and Mihai Surdeanu.   \ti{Swanson linking revisited: Accelerating literature-based discovery across domains using a conceptual influence graph}.   In \ve{Proceedings of the Conference of the Association for Computational Linguistics: Software Demonstrations (ACL)}, 2017.

\item
Rebecca Sharp, Mihai Surdeanu, Peter Jansen, Peter Clark, and Michael Hammond.  \ti{Creating Causal Embeddings for Question Answering with Minimal Supervision}.  In \ve{Proceedings of the conference on Empirical Methods in Natural Language Processing (EMNLP)}, 2016.

\item
Peter Jansen, Niranjan Balasubramanian, Mihai Surdeanu, and Peter Clark.  \ti{What's in an Explanation? Characterizing Knowledge and Inference Requirements for Elementary Science Exams}.  In \ve{Proceedings of the 26th International Conference on Computational Linguistics (COLING)}, 2016.

\item
Mihai Surdeanu, Thomas Hicks, and Marco A. Valenzuela-Escarcega.  \ti{Two Practical Rhetorical Structure Theory Parsers}. \ve{Proceedings of the Conference of the North American Chapter of the Association for Computational Linguistics - Human Language Technologies: Software Demonstrations (NAACL HLT)}, 2015. 

\item
Rebecca Sharp, Peter Jansen, Mihai Surdeanu, and Peter Clark.  \ti{Spinning Straw into Gold: Using Free Text to Train Monolingual Alignment Models for Non-factoid Question Answering}.  In \ve{Proceedings of the Conference of the North American Chapter of the Association for Computational Linguistics - Human Language Technologies (NAACL HLT)}, 2015. 

\item
Ander Intxaurrondo, Eneko Agirre, Oier Lopez de Lacalle, and Mihai Surdeanu.  \ti{Diamonds in the Rough: Event Extraction from Imperfect Microblog Data}.  In \ve{Proceedings of the Conference of the North American Chapter of the Association for Computational Linguistics - Human Language Technologies (NAACL HLT)}, 2015.

\item
Marco A. Valenzuela-Escarcega, Gustave Hahn-Powell, Thomas Hicks, and Mihai Surdeanu.  \ti{A Domain-independent Rule-based Framework for Event Extraction}.  In \ve{Proceedings of the 53rd Annual Meeting of the Association for Computational Linguistics and the 7th International Joint Conference on Natural Language Processing of the Assian Federation of Natural Language Processing: Software Demonstrations (ACL-IJCNLP)}, 2015.

\item
Daniel Fried, Mihai Surdeanu, Stephen Kobourov, Melanie Hingle, and Dane Bell.  \ti{Analyzing the Language of Food on Social Media}.  In \ve{Proceedings of the 2014 IEEE International Conference on Big Data (IEEE BigData)}, 2014.

\item
Anh Tran, Mihai Surdeanu, and Paul Cohen.  \ti{Extracting Latent Attributes from Video Scenes Using Text as Background Knowledge}.  In \ve{Proceedings of the Third Joint Conference on Lexical and Computational Semantics (*SEM)}, 2014.

\item
Christopher D. Manning, Mihai Surdeanu, John Bauer, Jenny Finkel, Steven J. Bethard, and David McClosky.  \ti{The Stanford CoreNLP Natural Language Processing Toolkit}.  In \ve{Proceedings of the 52nd Annual Meeting of the Association for Computational Linguistics (ACL)}, 2014 [most cited paper at this conference, as of April 2017].

\item
Peter Jansen, Mihai Surdeanu, and Peter Clark.  \ti{Discourse Complements Lexical Semantics for Non-factoid Answer Reranking}.  In \ve{Proceedings of the 52nd Annual Meeting of the Association for Computational Linguistics (ACL)}, 2014.

\item
Mihai Surdeanu and Sara Jeruss.  \ti{Identifying Patent Monetization Entities}.  In \ve{Proceedings of the XIV International Conference on Artificial Intelligence and Law (ICAIL)}, 2013.

\item
Mihai Surdeanu, Julie Tibshirani, Ramesh Nallapati, Christopher D. Manning.  \ti{Multi-instance Multi-label Learning for Relation Extraction}.  In \ve{Proceedings of the 2012 Conference on Empirical Methods in Natural Language Processing and Natural Language Learning (EMNLP-CoNLL)}, 2012 [third most cited paper at this conference, as of April 2017].

\item
Heeyoung Lee, Marta Recasens, Angel Chang, Mihai Surdeanu, Dan Jurafsky.  \ti{Joint Entity and Event Coreference Resolution across Documents}.  In \ve{Proceedings of the 2012 Conference on Empirical Methods in Natural Language Processing and Natural Language Learning (EMNLP-CoNLL)}, 2012.

\item
Mihai Surdeanu, Ramesh Nallapati, George Gregory, Joshua Walker, and Christopher D. Manning.  \ti{Risk Analysis for Intellectual Property Litigation}.  In \ve{Proceedings of the Thirteenth International Conference on Artificial Intelligence and Law (ICAIL)}, 2011.

\item
David McClosky, Mihai Surdeanu, and Christopher D. Manning.  \ti{Event Extraction as Dependency Parsing}.  In \ve{Proceedings of the 49th Annual Meeting of the Association for Computational Linguistics: Human Language Technologies (ACL)}, 2011.

\item
K. Raghunathan, H. Lee, S. Rangarajan, N. Chambers, M. Surdeanu, D. Jurafsky, C. D. Manning.  \ti{A Multi-Pass Sieve for Coreference Resolution}. In \ve{Proceedings of the 2010 Conference on Empirical Methods in Natural Language Processing (EMNLP)}, 2010 [second most cited paper at this conference, as of April 2017].

\item
M. Surdeanu and C. D. Manning.  \ti{Ensemble Models for Dependency Parsing: Cheap and Good?}Ê In \ve{Proceedings of the North American Chapter of the Association for Computational Linguistics Conference (NAACL)}, 2010. (This paper was a finalist for the best short paper award.)

\item
B. Zapirain, E. Agirre, L. Marquez and M. Surdeanu.  \ti{Improving Semantic Role Classification with Selectional Preferences}.  In \ve{Proceedings of the North American Chapter of the Association for Computational Linguistics Conference (NAACL)}, 2010.

\item
J. Hajic, M. Ciaramita, R. Johansson, D. Kawahara, M. Marti, L. Marquez, A. Meyers, J. Nivre, S. Pado, J. Stepanek, P. Stranak, M. Surdeanu, N. Xue, and Y. Zhang.  \ti{The CoNLL-2009 Shared Task: Syntactic and Semantic Dependencies in Multiple Languages}.  In \ve{Proceedings of the 13th Conference on Computational Natural Language Learning (CoNLL-2009)}, 2009.

\item
Katja Filippova, Mihai Surdeanu, Massimiliano Ciaramita, Hugo Zaragoza.  \ti{Company-Oriented Extractive Summarization of Financial News}.  In \ve{Proceedings of 12th Conference of the European Chapter of the Association for Computational Linguistics (ACL)}, 2009.

\item
Mihai Surdeanu, Richard Johansson, Adam Meyers, Lluis Marquez and Joakim Nivre.  \ti{The CoNLL-2008 Shared Task on Joint Parsing of Syntactic and Semantic Dependencies}.  In \ve{Proceedings of the 12th Conference on Computational Natural Language Learning (CoNLL-2008)}, 2008.

\item
Mihai Surdeanu, Massimiliano Ciaramita, and Hugo Zaragoza.  \ti{Learning to Rank Answers on Large Online QA Collections}.  In \ve{Proceedings of the 46th Annual Meeting of the Association for Computational Linguistics (ACL)}, 2008. 

\item
David Dominguez-Sal, Mihai Surdeanu, Josep Aguilar-Saborit, and Josep Lluis Larriba-Pey.  \ti{Cache-aware load balancing for question answering}.  In \ve{Proceedings of the 17th ACM Conference on Information and Knowledge Management (CIKM)}, 2008. 

\item
David Dominguez-Sal, Josep Lluis Larriba-Pey, and Mihai Surdeanu.  \ti{A Multi-layer Collaborative Cache for Question Answering}.  In \ve{Proceedings of Euro-Par}, 2007.

\item
Mihai Surdeanu, David Dominguez-Sal, and Pere Comas.  \ti{Performance Analysis of a Factoid Question Answering System for Spontaneous Speech Transcriptions}.  In \ve{Proceedings of the 10th International Conference on Speech Communication and Technology (Interspeech)}, 2006.

\item
Lluis Marquez, Mihai Surdeanu, Pere Comas, and Jordi Turmo.  \ti{A Robust Combination Strategy for Semantic Role Labeling}.  In \ve{Proceedings of Human Language Technology/Empirical Methods for Natural Language Processing (HLT/EMNLP)}, 2005.

\item
Mihai Surdeanu, Jordi Turmo and Elizabeth Comelles.  \ti{Named Entity Recognition from Spontaneous Open-Domain Speech}.  In \ve{Proceedings of the 9th European Conference on Speech Communication and Technology (Interspeech)}, 2005.

\item
Mihai Surdeanu, Jordi Turmo, and Alicia Ageno.  \ti{A Hybrid Unsupervised Approach for Document Clustering}.  In \ve{Proceedings of the Eleventh ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (KDD)}, 2005.

\item
Mihai Surdeanu, Sanda Harabagiu, John Williams and Paul Aarseth.  \ti{Using Predicate Argument Structures for Information Extraction}.  In \ve{Proceedings of the 41st Annual Meeting of the Association for Computational Linguistics (ACL)}, 2003 [second most cited paper at this conference, as of April 2017]. 

\item
Mihai Surdeanu and Sanda Harabagiu.  \ti{Infrastructure for Open-Domain Information Extraction}.  In \ve{Proceedings of Human Language Technology (HLT) Conference}, 2002.

\item
Dan Moldovan, Sanda Harabagiu, Marius Pasca, and Mihai Surdeanu.  \ti{Performance Issues and Error Analysis in an Open-Domain Question Answering System}.  In \ve{Proceedings of the 40th Annual Meeting of the Association for Computational Linguistics (ACL)}, 2002.

\item
[* \addtocounter{enumi}{1}\theenumi ]
Sanda Harabagiu, Dan Moldovan, Marius Pasca, Rada Mihalcea, Mihai Surdeanu, Razvan Bunescu, Roxana Girju, Vasile Rus, and Paul Morarescu.  \ti{The Role of Lexico-Semantic Feedbacks in Open-Domain Textual Question/Answering}.  In \ve{Proceedings of the 39th Association for Computational Linguistics (ACL)}, 2001. 

\item
[* \addtocounter{enumi}{1}\theenumi ]
Mihai Surdeanu, Dan Moldovan, and Sanda Harabagiu.  \ti{Performance Analysis of a Distributed Question/Answering System}.  In \ve{Proceedings of the 15th International Parallel and Distributed Processing Symposium (IPDPS)}, 2001.

\item
[* \addtocounter{enumi}{1}\theenumi ]
Mihai Surdeanu.  \ti{Distributed Java Virtual Machine for Message Passing Architectures}.  In \ve{Proceedings of the 2000 International Conference on Distributed Systems (ICDS)}, 2000.



\end{enumerate}

\item [Less Competitive Peer-Reviewed Conference and Workshop Publications]\
%(all authors listed in alphabetical order)]\ 

(Publications preceded by * are substantively based on work done as a graduate student)

\begin{enumerate}
\setcounter{enumi}{51}

\item
Dane Bell, Daniel Fried, Luwen Huangfu, Mihai Surdeanu, and Stephen Kobourov.  \ti{Towards Using Social Media to Identify Individuals at Risk for Preventable Chronic Illness}.  In \ve{Proceedings of the 10th edition of the Language Resources and Evaluation Conference (LREC)}, 2016.

\item
Dane Bell, Gustave Hahn-Powell, Marco A. Valenzuela-Escarcega, and Mihai Surdeanu.  \ti{An Investigation of Coreference Phenomena in the Biomedical Domain}.  In \ve{Proceedings of the 10th edition of the Language Resources and Evaluation Conference (LREC)}, 2016.

\item
Marco A. Valenzuela-Escarcega, Gustave Hahn-Powell, and Mihai Surdeanu.  \ti{Odin's Runes: A Rule Language for Information Extraction}.  In \ve{Proceedings of the 10th edition of the Language Resources and Evaluation Conference (LREC)}, 2016.

\item
Marco A. Valenzuela-Escarcega, Gustave Hahn-Powell, Dane Bell, and Mihai Surdeanu.  \ti{SnapToGrid: From Statistical to Interpretable Models for Biomedical Information Extraction}.  In \ve{Proceedings of the 2016 Workshop on Biomedical Natural Language Processing (BioNLP 2016)}, 2016.

\item
Gustave Hahn-Powell, Dane Bell, Marco A. Valenzuela-Escarcega, and Mihai Surdeanu.  \ti{This before That: Causal Precedence in the Biomedical Domain}.  In \ve{Proceedings of the 2016 Workshop on Biomedical Natural Language Processing (BioNLP 2016)}, 2016.

\item
Heeyoung Lee, Mihai Surdeanu, Bill MacCartney, and Dan Jurafsky.  \ti{On the Importance of Text Analysis for Stock Price Prediction}.  In \ve{Proceedings of the 9th edition of the Language Resources and Evaluation Conference (LREC)}, 2014.

\item
Kevin Reschke, Martin Jankowiak, Mihai Surdeanu, Christopher D. Manning, and Daniel Jurafsky.  \ti{Event Extraction Using Distant Supervision}.  In \ve{Proceedings of the 9th edition of the Language Resources and Evaluation Conference (LREC)}, 2014.

\item
Mihai Surdeanu and Heng Ji.  \ti{Overview of the English Slot Filling Track at the TAC2014 Knowledge Base Population Evaluation}.  In \ve{Proceedings of the TAC-KBP 2014 Workshop}, 2014.

\item
Mihai Surdeanu.  \ti{Overview of the TAC2013 Knowledge Base Population Evaluation: English Slot Filling and Temporal Slot Filling}.  In \ve{Proceedings of the TAC-KBP 2013 Workshop}, 2013.

\item
Angus Forbes, Mihai Surdeanu, Peter Jansen, and Jane Carrington.  \ti{Transmitting Narrative: An Interactive Shift-Summarization Tool for Improving Nurse Communication}.  In \ve{Proceedings of the 3rd IEEE Workshop on Interactive Visual Text Analytics}, 2013.

\item
David McClosky, Mihai Surdeanu, and Christopher D. Manning.  \ti{Event Extraction as Dependency Parsing for BioNLP 2011}.  In \ve{Proceedings of the BioNLP Workshop}, 2011.

\item
Sebastian Riedel, David McClosky, Mihai Surdeanu, Andrew McCallum, Christopher D. Manning.  \ti{Model Combination for Event Extraction in BioNLP 2011}.  In \ve{Proceedings of the BioNLP Workshop}, 2011.

\item
Mihai Surdeanu, David McClosky, Mason R. Smith, Andrey Gusev, and Christopher D. Manning.  \ti{Customizing an Information Extraction System to a New Domain}.  In \ve{Proceedings of the Workshop on Relational Models of Semantics}, 2011.

\item
Heeyoung Lee, Yves Peirsman, Angel Chang, Nathanael Chambers, Mihai Surdeanu, Dan Jurafsky. ti{Stanford's Multi-Pass Sieve Coreference Resolution System at the CoNLL-2011 Shared Task}.  In \ve{Proceedings of the CoNLL-2011 Shared Task}, 2011.

\item
Mihai Surdeanu, Sonal Gupta, John Bauer, David McClosky, Angel X. Chang, Valentin I. Spitkovsky, Christopher D. Manning.  \ti{StanfordÕs distantly-supervised slot-filling system}.Ê In \ve{Proceedings of the TAC-KBP 2011 Workshop}, 2011.

\item
R. Nallapati, M. Surdeanu, and C. D. Manning.  \ti{Blind Domain Transfer for Named Entity Recognition using Generative Latent Topic Models}.Ê In \ve{Proceedings of the NIPS 2010 Workshop on Transfer Learning Via Rich Generative Models}, 2010.

\item
Mihai Surdeanu, David McClosky, Julie Tibshirani, John Bauer, Angel X. Chang, Valentin I. Spitkovsky, Christopher D. Manning.  \ti{A Simple Distant Supervision Approach for the TAC-KBP Slot Filling Task}.Ê In \ve{Proceedings of the TAC-KBP 2010 Workshop}, 2010.

\item
M. Surdeanu, R. Nallapati, and C. D. Manning.Ê  \ti{Legal Claim Identification: Information Extraction with Hierarchically Labeled Data}.  In \ve{Proceedings of the LREC 2010 Workshop on the Semantic Processing of Legal Texts (SPLeT)}, 2010.

\item
Ramesh Nallapati, Mihai Surdeanu, and Christopher D. Manning.  \ti{CorrActive Learning: Learning from Noisy Data through Human Interaction}.  In \ve{Proceedings of the IJCAI Workshop on Intelligence and Interaction}, 2009.

\item
Mihai Surdeanu, Roser Morante, and Lluis Marquez.  \ti{Analysis of Joint Inference Strategies for the Semantic Role Labeling of Spanish and Catalan}.  In \ve{Proceedings of the 9th International Conference on Intelligent Text Processing and Computational Linguistics (CICLing)}, 2008.

\item
Massimiliano Ciaramita, Giuseppe Attardi, Felice Dell'Orletta, and Mihai Surdeanu.  \ti{DeSRL: A Linear-Time Semantic Role Labeling System}. In {Proceedings of the Shared Task of the 12th Conference on Computational Natural Language Learning (CoNLL)}, 2008.

\item
Jordi Poveda, Mihai Surdeanu, and Jordi Turmo.  \ti{A Comparison of Statistical and Rule-Induction Learners for Automatic Tagging of Time Expressions in English}.  In \ve{Proceedings of the 14th International Symposium on Temporal Representation and Reasoning}, 2007.

\item
Pere R. Comas, Jordi Turmo, and Mihai Surdeanu.  \ti{Robust Question Answering for Speech Transcripts Using Minimal Syntactic Analysis}.  In \ve{Proceedings of the Cross Language Evaluation Forum Workshop}, 2007.

\item
Lluis Marquez, Lluis Padro, Mihai Surdeanu, and Luis Villarejo.  \ti{UPC: Experiments with Joint Learning within SemEval Task 9}.  In \ve{Proceedings of the SemEval 2007 Workshop}, 2007.

\item
Mihai Surdeanu and Massimiliano Ciaramita.  \ti{Robust Information Extraction with Perceptrons}.  In \ve{Proceedings of the NIST 2007 Automatic Content Extraction Workshop (ACE)}, 2007.

\item
David Farwell, Jesus Gimenez, Edgar Gonzalez, Reda Halkoum, Horacio Rodriguez, and Mihai Surdeanu.  \ti{The UPC System for Arabic-to-English Entity Translation}.  In \ve{Proceedings of the NIST 2007 Automatic Content Extraction Workshop (ACE)}, 2007. 

\item
Xavier Carreras, Mihai Surdeanu, and Lluis Marquez.  \ti{Projective Dependency Parsing with Perceptron}.  In \ve{Proceedings of CoNLL-2006 Shared Task}, 2006.

\item
Mihai Surdeanu, Jordi Turmo, and Alicia Ageno.  \ti{A Hybrid Approach for the Acquisition of Information Extraction Patterns}.  In \ve{Proceedings of the EACL 2006 Workshop on Adaptive Text Extraction and Mining (ATEM)}, 2006.

\item
Mihai Surdeanu and Jordi Turmo.  \ti{Semantic role labeling using complete syntactic analysis}.  In \ve{Proceedings of the CoNLL-2005 Shared Task}, 2005. 

\item
Daniel Ferres, Sameer Kanaan, David Dominguez-Sal, Edgar Gonzales, Alicia Ageno, Maria Fuentes, Horacio Rodriguez, Mihai Surdeanu, and Jordi Turmo.  \ti{TALP-UPC at TREC 2005: Experiments Using a Voting Scheme Among Three Heterogeneous QA Systems}.  In \ve{Proceedings of the Fourteenth Text REtrieval Conference (TREC)}, 2005.

\item
Daniel Ferres, Sameer Kanaan, Edgar Gonzales, Alicia Ageno, Horacio Rodriguez, Mihai Surdeanu, and Jordi Turmo.  \ti{TALP-QA System at TREC 2004: Structural and Hierarchical Relaxing of Semantic Constraints}.  In \ve{Proceedings of the Thirteenth Text REtrieval Conference (TREC)}, 2004.

\item
[* \addtocounter{enumi}{1}\theenumi ]
Sanda Harabagiu, Mihai Surdeanu, and Paul Morarescu.  \ti{Automatic Discovery of Linguistic Patterns for Information Extraction}.  In \ve{Proceedings of the 14th International FLAIRS Conference}, 2001.

\item
[* \addtocounter{enumi}{1}\theenumi ]
Sanda Harabagiu, Dan Moldovan, Marius Pasca, Mihai Surdeanu, Rada Mihalcea, Roxana Girju, Vasile Rus, Finley Lacatusu, Paul Morarescu, and Razvan Bunescu.  \ti{Answering complex, list and context questions with LCC's Question-Answering Server}.  In \ve{Proceedings of the 10th Text REtrieval Conference (TREC)}, 2001.

\item
[* \addtocounter{enumi}{1}\theenumi ]
Sanda Harabagiu, Dan Moldovan, Marius Pasca, Rada Mihalcea, Mihai Surdeanu, Razvan Bunescu, Roxana Girju, Vasile Rus, and Paul Morarescu.  \ti{FALCON: Boosting Knowledge for Answer Engines}.  In \ve{Proceedings of the Text Retrieval Conference (TREC)}, 2000. 

\item
[* \addtocounter{enumi}{1}\theenumi ]
Mihai Surdeanu.  \ti{DISK: A Distributed Java Virtual Machine for DSP Architectures}.  In \ve{Proceedings of DSPS FEST}, 1999.


\end{enumerate}


\item [Work in Progress] (cited from the research statement)\
\begin{enumerate}
\setcounter{enumi}{86}

\item 
Marco A. Valenzuela-Escarcega, Ozgun Babur, Gustave Hahn-Powell, Dane Bell, Thomas Hicks, Enrique Noriega-Atala, Mihai Surdeanu, Emek Demir, and Clayton Morrison.  \ti{Large-scale Automated Reading of Scientific Cancer Literature can Discover New  Cancer Driving Mechanisms}. To be submitted to \ve{Bioinformatics}, May 2017.

\item
Marco A. Valenzuela-Escarcega, Ajay Nagesh, and Mihai Surdeanu.  \ti{Bootstrapped Representation Learning for Lexicon Acquisition}.  Submitted to the \ve{Conference on Empirical Methods in Natural Language Processing (EMNLP)}, April 2017.

\item
Rebecca Sharp, Mihai Surdeanu, Peter Jansen, Peter Clark.  \ti{Tell Me Why: Using Question Answering as Distant Supervision for Answer Justification}. Submitted to the \ve{Conference on Empirical Methods in Natural Language Processing (EMNLP)}, April 2017.

\item 
Dane Bell, Ajay Nagesh, Egoitz Laparra, Mihai Surdeanu, Melanie Hingle, Stephen Kobourov. \ti{Detecting Weight Status from Twitter Activity}. Submitted to the \ve{Conference on Empirical Methods in Natural Language Processing (EMNLP)}, April 2017.


\end{enumerate}


\item [Patents] \
\begin{enumerate}
%\setcounter{enumi}{63}

\item 
Mihai Surdeanu, Marco A. Valenzuela-Escarcega, Gustave Hahn-Powell, Dane Bell, Thomas Hicks, Enrique Noriega, Clayton Morrison. \ti{Method for Extracting and Assessing Signaling Pathways from Biomedical Literature}. Provisional US patent filed on 03/2017.

\item 
Mihai Surdeanu, Sara E. Jeruss, and Joshua Walker. \ti{Systems and Methods for Classifying Entities}. US patent filed on 03/2014. 

\item 
Mihai Surdeanu, Ingrid Kaldre, Carla Rydholm, Ramesh Nallapati, Ben Bangert, Joshua Walker, George Gregory, Gavin Carothers, and Nick Pilon. \ti{Systems and Methods for Using Non-textual Information in Analyzing Patent Matters}. US patent filed on 03/2013.

\end{enumerate}


\item [Invited Scholarly Presentations] \lmt \
\begin{enumerate}

\item Keynote at the Intl. Conf. on Natural Language and Information Systems (NLDB), june 2107
\item Bill and Melinda Gates Foundation, February 2017
\item Harvard Medical School, Harvard University, November 2016
\item Bill and Melinda Gates Foundation, October 2016
\item Technical University of Cluj-Napoca, May 2016
\item Paul Allen Institute for Artificial Intelligence, October 2013
\end{enumerate}

\item [Conference Presentations] \lmt \

(\& indicates talks/posters co-presented with students, postdocs, or collaborators. \% indicates talks/posters presented solely by students, postdocs, or collaborators)


\begin{enumerate}

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
International Conference on Computational Linguistics (COLING), 2016

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Empirical Methods in Natural Language Processing (EMNLP), 2016

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Workshop on Biomedical Natural Language Processing (BioNLP), 2016

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Language Resources and Evaluation Conference (LREC), 2016

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Annual meeting of the Association for Computational Linguistics (ACL), 2015

\item 
[\& \addtocounter{enumi}{1}\theenumi ]
North American Chapter of the Association for Computational Linguistics - Human Language Technologies (NAACL HLT), 2015

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Third Joint Conference on Lexical and Computational Semantics (*SEM), 2014

\item 
[\& \addtocounter{enumi}{1}\theenumi ]
Annual Meeting of the Association for Computational Linguistics (ACL), 2014

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Language Resources and Evaluation Conference (LREC), 2014

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Congreso de la Sociedad Espa\~{n}ola para el Procesamiento del Lenguaje Natural (SEPLN), 2014

\item 
International Conference on Artificial Intelligence and Law (ICAIL), 2013

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
IEEE Workshop on Interactive Visual Text Analytics, 2013

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
NIST TAC-KBP 2013 Workshop, 2014

\item 
NIST TAC-KBP 2013 Workshop, 2013


\end{enumerate}


\item [Colloquium Presentations]\

\begin{enumerate}
\item UA College of ScienceÕs Science Cafe, Fall 2016
\item UA Honors College Smart Talk, Spring 2015
\item UA Linguistics colloquium, Fall 2014
\item UA Cognitive Science colloquium, Fall 2014
\item UA Computer Science colloquium, Spring 2013
\item UA Linguistics colloquium, Spring 2013
\end{enumerate}

\item [Open-Source Software]\

\begin{enumerate}

\item REACH: biomedical information extraction suite
\begin{itemize}
\item \url{https://github.com/clulab/reach}
\item Top performer in the machine reading evaluation organized by the DARPA Big Mechanism program
\end{itemize}

\item Processors: NLP suite in Scala
\begin{itemize}
\item \url{https://github.com/clulab/processors }
\end{itemize}

\item CoreNLP: Stanford NLP software suite
\begin{itemize}
\item \url{https://stanfordnlp.github.io/CoreNLP/}
\item Downloads in the tens of thousands
\end{itemize}

\item Multi-instance multi-label relation extraction
\begin{itemize}
\item \url{https://nlp.stanford.edu/software/mimlre.shtml}
\end{itemize}

\item SBEP: Stanford Biomedical Event Parser 
\begin{itemize}
\item \url{https://nlp.stanford.edu/software/eventparser.shtml}
\end{itemize}

\item Ensemble: Linearly-interpolated Dependency Parsers
\begin{itemize}
\item \url{http://www.surdeanu.info/mihai/ensemble/ }
\end{itemize}

\item Swirl: the Semantic Role Labeler
\begin{itemize}
\item \url{http://www.surdeanu.info/mihai/swirl/}
\end{itemize}

\item Bios: Suite of Syntactico-Semantic Analyzers
\begin{itemize}
\item \url{http://www.surdeanu.info/mihai/bios/ }
\end{itemize}

\item Spear: Syntactic Parser
\begin{itemize}
\item \url{http://www.surdeanu.info/mihai/spear/ }
\end{itemize}

\end{enumerate}


\item [Grants]\
\begin{enumerate}

\item \ti{An Exploratory System for Complex World Modeling}, \ve{DARPA} -- subcontract from the Florida Institute for Human and Machine Cognition (IHMC). Sole PI at UA. \$149K, 2017 -- 18, 8\% effort

\item \ti{Development of Causal Models with the Aid of Natural Language Processing (NLP) Technology}, \ve{Bill and Melinda Gates Foundation}. Sole PI. \$313K, 2016 -- 17, 16\% effort

\item \ti{Large-scale Non-invasive Detection of Type 2 Diabetes Risk through Machine Learning and Visualization on Social Media}, \ve{Accelerate for Success Program, University of Arizona}. PI, other co-PIs: Stephen Kobourov, Melanie Hingle, and Stephen Rains. \$97K, 2017

\item \ti{REACH: Reading and Assembling Contextual and Holistic Mechanisms from Text}, \ve{DARPA}. PI, other co-PIs: Kobus Barnard, Clayton Morrison, Angus Forbes, Ryan Gutenkunst, and Guang Yao. \$3.6M, 2014 -- 2017, 19\% effort

\item \ti{Enhancing Nurse Decision-Making via Augmented Communication Tools (ACTs)}, \ve{NIH}. PI: Jane Carrington, co-PIs: Mihai Surdeanu, Angus Forbes. \$745K, 2014 -- 2017, 8\% effort

\item \ti{Robust Approximate Inference for Question Answering}, \ve{Allen Institute for Artificial Intelligence}. Sole PI. \$149K, 2013 -- 2015, 10\% effort

\item \ti{Question Answering Using Linguistics Features and Discourse Modeling}, \ve{Allen Institute for Artificial Intelligence}. Sole PI. \$90K, 2013, 16\% effort

\end{enumerate}

\vspace{-.1cm}\item [Courses Developed, Revised, and Taught]\
	
Text Retrieval and Web Search (developed and taught at UA)\\
Applied Natural Language Processing  (developed and taught at UA)\\
Statistical Foundations for the Information Age (revised and taught at UA)\\
Advanced Topics in Computational Intelligence Seminar (developed and taught at UA)

\vspace{-.1cm}\item [Postdoc~Advisees]\

Ajay Nagesh, 2017 -- present\\
March Valenzuela, 2016 -- present\\
Peter Jansen, 2013 -- 2015, currently tenure-track faculty in the School of Information at UA

\vspace{-.1cm}\item [Ph.D.~(Co)Advisees]\

Mithun Paul, CS, 1st year \\
Joshua Meyer, Linguistics, co-advised with T. Beaver, expected graduation Summer 2018 \\
Dane Bell, Linguistics, co-advised with A. Wedel, expected graduation Spring 2018 \\
Gustave Hahn-Powell, Linguistics, co-advised with S. Fong, expected graduation Spring 2018 \\
Rebecca Sharp, Linguistics, co-advised with M. Hammond, expected graduation Summer 2017 \\
Marco Valenzuela, CS, graduated Spring 2016 \\
Heeyoung Lee, Stanford Linguistics, co-advised with D. Jurafsky, graduated Spring 2016 \\
Anh Tran, CS, co-advised with P. Cohen, graduated Summer 2014

\vspace{-.1cm}\item [M.S.~Thesis (Co)Supervision ]\
%(12 refereed publications with MS co-authors)]\

Benjamin Gaska, CS, co-advised with M. Strout, expected graduation Spring 2017\\
Rebecca Sharp, Linguistics, graduated Spring 2014 \\
Gustave Hahn-Powell, Linguistics, graduated Spring 2014 

\vspace{-.1cm}\item [Honors Thesis Supervision ]\

Katherine Fackrell, SISTA, Spring 2015 \\
Daniel Fried, CS/SISTA, Spring 2014

\vspace{-.1cm}\item [Service on PhD Dissertation Committees other than Advisor ]\

Glen Pink, CS University of Sydney, expected graduation Spring 2017 \\
Yekaterina Kharitonova, CS, graduated Spring 2016 \\
Jeremy Wright, CS, graduated Spring 2015 

\newpage
\vspace{-.1cm}\item [List of Collaborators ] (excluding advisees, past 5 years)\

\begin{center}
 \begin{tabular}{l|l|l|l}
 {\bf Last Name} & {\bf First Name} & {\bf Relation} & {\bf Current Institution} \\
 \hline
Agirre & Eneko & Co-author & University of Basque Country \\
%\hline
Balasubramanian & Niranjan & Co-author & Stony Brook University \\
Barnard & Kobus & Co-author & University of Arizona \\
Bauer & John & Co-author & Stanford University \\
Bethard & Steven & Co-author & University of Arizona \\
Carrington & Jane & Co-author & University of Arizona \\
Chambers & Nate & Co-author & US Naval Academy \\
Chang & Angel & Co-author & Google \\
Clark & Peter & Co-author & Allen Institute for AI \\
Cohen & Paul & Co-author & DARPA/University of Arizona \\
Dawson & Colin & Co-author & Oberlin College \\
De Lacalle & Oier Lopez & Co-author & University of Basque Country \\
Del Pero & Luca & Co-author & University of Arizona \\
Finkel & Jenny & Co-author & Prismatic \\
Forbes & Angus & Co-author & University of Illinois \\
Hammond & Mike & Co-author & University of Arizona \\
Hicks & Thomas & Co-author & University of Arizona \\
Hingle & Melanie & Co-author & University of Arizona \\
Intxaurrondo & Ander & Co-author & University of Basque Country \\
Jankowiak & Martin & Co-author & Stanford University \\
Jansen & Peter & Co-author & University of Arizona \\
Jeruss & Sara & Co-author & Facebook \\
Ji & Heng & Co-author & Rensselaer Polytechnic Institute \\
Johansson & Richard & Co-author & University of Gothenburg \\
Jurafsky & Dan & Co-author & Stanford University \\
Kobourov & Stephen & Co-author & University of Arizona \\
MacCartney & Bill & Co-author & Google \\
Manning & Christopher & Co-author & Stanford University \\
McCallum & Andrew & Co-author & University of Massachusetts  \\
McClosky & David & Co-author & Google  \\
Morrison & Clayton & Co-author &  University of Arizona \\
Nallapati & Ramesh & Co-author & IBM \\
Peirsman &  Yves & Co-author & University of Leuven \\
Recasens & Marta & Co-author & Google \\
Reschke & Kevin & Co-author & Stanford University \\
Riedel & Sebastian & Co-author & University College London \\
Tibshirani & Julie & Co-author & Stanford University \\
Zapirain & Benat & Co-author & University of Basque Country \\


\end{tabular}
\end{center}


\end{description}

\end{document}




