\def\pilot{{\tt PILOT}}
\def\RR{{\tt SAIL}}
\def\bb{\noindent\hspace{.46cm}$\bullet$\hspace{.19cm}}


\UseRawInputEncoding

\documentclass[10pt]{article}

%\usepackage{simplemargins}
%\setallmargins{1in}

\usepackage{url}
\evensidemargin -.2cm
\oddsidemargin -.2cm
\setlength\topmargin{-0.7in}
\setlength{\textwidth}{16cm}   % width of body
\setlength{\textheight}{9.2in}   % heigth of body
%\setlength{\sectionskip}{2ex}
\setlength{\itemsep}{-1in}
\setlength{\leftmarginii}{.05in}

\newcommand{\ve}[1]{{\em #1}} % venue of publication
\newcommand{\ti}[1]{``#1''} % title of publication
\newcommand{\lmt}{(limited to period starting 01/2013)}

\begin{document}


%\pagestyle{empty}

\begin{center}
{\Large \bf CURRICULUM VITAE\\
\bigskip{\large \bf Mitch Paul Mithun}}
\end{center}
\smallskip

 \makebox{
    \parbox{2.6in}{\centering
    {\small
    Department of Computer Science\\
    University of Arizona\\
    Tucson, AZ 85721\\
}
    }
  \nolinebreak
    \parbox{3.2in}{\centering
	{\small 

    Email: mithunpaul@email.arizona.edu \\
    Phone: (520) 395 5778	}
    \url{www2.cs.arizona.edu/people/mithunpaul/} \\
    	\url{https://github.com/mithunpaul08}
 }}
\bigskip

\begin{description}

\item [Education]\

\begin{tabular}{lp{4.5in}}
\hspace{-.2cm}2015 -- Present &  Ph.D.~Computer Science, {\sc University of Arizona}
\\\vspace{.0cm}&Thesis: Knowledge Distillation As A Solution For Domain Transfer.
\\\vspace{.1cm}& Adviser: Mihai~Surdeanu\\
\vspace{.1cm}\hspace{-.2cm}2014 &  M.S.~Computer Science, {\sc University of Arizona, Tucson, USA} \\
\vspace{.1cm}\hspace{-.2cm}2005 &  M.S.~Physics, {\sc Birla Institute of Technology and Science (BITS), Pilani, India} \\
\hspace{-.2cm}2005 & B.S.~Chemical Engineering,  {\sc Birla Institute of Technology and Science (BITS), Pilani, India}
\end{tabular}


\item [Professional Experience]\

\begin{tabular}{lp{4.9in}}


\hspace{-.2cm}2014 -- 2015 & Software Engineer\\\vspace{.1cm}
& {\sc Intel Corporation} \\

\hspace{-.2cm}2013 -- 2013 & Summer Intern\\\vspace{.1cm}
& {\sc The Goldman Sachs Group, Inc.} \\

\hspace{-.2cm}2011 -- 2012 & Technology Lead (Research)\\\vspace{.1cm}
&  {\sc Infosys Labs, India} \\

\hspace{-.2cm}2008 -- 2011 & Technology Associate (Research)\\\vspace{.1cm}
& {\sc Infosys Labs, India} \\

\hspace{-.2cm}2005 -- 2008 & Software Engineer	\\
& {\sc Infosys Ltd, India}
\end{tabular}

\item [Patents] \
\begin{enumerate}


\item
Ashutosh Saxena, Vishal Krishna Saxena, Kaushal Saxena, Kumar Surni, Mithun Paul. \ti{Method and System for Providing Masking Services}.  US patent No. US8881224B2.
\item
Ashutosh Saxena, Mithun Paul. \ti{System and method for deletion of data in a remote computing platform}.  US patent No. US8504532B2.
\item
Sravan R, Mithun Paul, Ashutosh Saxena. \ti{Methods for dynamic destruction of data in a remote data storage platform and devices thereof}.  US patent No. US9740726B2.
\item
Mithun Paul, Sandeep Suntwal, Rebecca Sharp, Mihai Surdeanu. \ti{System and method for cross domain fact verification}. (in progress).

\end{enumerate}
\bigskip
\item [ Peer-Reviewed  Publications]\


(* denotes equal contributions from the authors)

\begin{enumerate}




\item Mithun Paul Panenghat, Sandeep Suntwal and Mihai Surdeanu.   \ti{Data and Model Distillation as a Solution for Domain-transferable Fact Verification}. Submitted to the\ve {Conference of the North American Chapter of the Association for Computational Linguistics(NAACL)}, 2021.

\item Mithun Paul Panenghat, Sandeep Suntwal, Faiz Rafique, Rebecca Sharp, and Mihai Surdeanu.   \ti{Towards the Necessity for Debiasing Natural Language Inference Datasets}. in the \ve{ Proceedings of Language Resources and Evaluation Conference (LREC)}, 2020.

\item Sandeep Suntwal*, Mithun Paul*, Rebecca Sharp, and Mihai Surdeanu.   \ti{On the Importance of Delexicalization for Fact Verification}. In \ve{the Proceedings of the Empirical Methods in Natural Language Processing (EMNLP)}, 2019.

\item  Rebecca Sharp et al,   \ti{Eidos \& Delphi: From Free Text to Executable Causal Models}. In \ve{ the Proceedings Annual Conference of the North American Chapter of the Association for Computational Linguistics (NAACL-HLT)}, 2019.

\end{enumerate}


\begin{enumerate}
\setcounter{enumi}{2}




\item Sandeep Suntwal*, Mithun Paul*, Rebecca Sharp, and Mihai Surdeanu.   \ti{On the Importance of Delexicalization for Fact Verification}. In \ve{Proceedings of the BlackboxNLP Workshop}, 2019.

\item Mithun Paul, Rebecca Sharp and Mihai Surdeanu,.   \ti{A mostly unlexicalized model for recognizing textual entailment}. In \ve{Proceedings of the Fact Verification workshop}, 2018.

\item Rebecca Sharp, Mithun Paul, Ajay Nagesh, Dane  Bell, and Mihai Surdeanu.   \ti{Grounding Gradable Adjectives through Crowdsourcing}. In \ve{Proceedings of the eleventh edition of the Language Resources and Evaluation Conference (LREC)}, 2018.

\item Mithun Paul, Derek Bambauer and Christian Collberg.   \ti{A Possible Solution For Privacy Preserving Cloud Data Storage}. In \ve{Proceedings of IEEE International Conference on Cloud Computing}, 2015.

\item  Mithun Paul, Nitin Singh Chauhan and Ashutosh Saxena.   \ti{A Security Analysis of Smartphone Data Flow and feasible solutions for lawful interception}. In \ve{ Proceedings for the IEEE 7th International Conference on Information Assurance and Security}, 2011.

\item  Mithun Paul, M. Choudary Gorantla and Ashutosh Saxena.   \ti{Group Key Exchange with Non Linear Trust}. In \ve{ Proceedings for The IEEE Fifth International Conference on Internet Multimedia Systems Architecture and Applications}, 2011.

\item  Mithun Paul and Ashutosh Saxena.   \ti{Data Shredding Service For Cloud}, In \ve{  Proceedings of the 2nd International Conference on Services in Emerging Markets}. 2011.

\item  Mithun Paul and Ashutosh Saxena.   \ti{Proof Of Erasability For Ensuring Comprehensive Data Deletion In Cloud Computing}. In \ve{  Proceedings of the Third International Conference, Communications in Computer and Information Science}, 2010.

\item  Mithun Paul and Ashutosh Saxena.   \ti{Zero Data Remnance Proof in cloud Storage}. In \ve{  International Journal of Network Security \& Its Applications (IJNSA), Vol.2, No.4}, 2010.




\end{enumerate}





\bigskip

\vspace{-.3cm}
\item [Honors, Awards, and Memberships]\
\begin{itemize}
\itemsep-1em
\item Finalist, three minute thesis competition, University of Arizona, March 2018\\

\item Member of the team that ranked 4th at the Fake News Challenge shared task, 2017\\
\item Member of the honor society Phi Kappa Phi, 2012 -- 2014\\
\item Best research paper award, International Conference on Services in Emerging Markets, 2011\\
\item Most valuable player,  Infosys  Ltd., 2008\\
\item Member of the team that ranked 2nd at a national trivia challenge and invited for a dinner with the President of India, 2005\\
\item Junior Research Fellow, Indian Institute of Science, Bangalore (2001 – 2003)\\

\end{itemize}


\vspace{-.4cm}\item [Conference Reviews]\
\begin{itemize}
\itemsep-1em
\item Fact Extraction and Verification (FEVER) workshop, Empirical Methods in Natural Language Processing (EMNLP), 2018\\
\item Fact Extraction and Verification (FEVER) workshop, Empirical Methods in Natural Language Processing (EMNLP), 2019\\
\item Language Resources and Evaluation Conference (LREC), 2020\\

\end{itemize}




\newpage


\item [Invited Talks ]\
\begin{itemize}
\item School of Information colloquia, University of Arizona, Nov 2019
\item Department of Computer Science colloquia, University of Arizona, Sep 2019
\item March for Science, AZ, Tucson , Arizona, Feb 2019
\item Three minute thesis competition, University of Arizona, March 2018
\end{itemize}



\item [Technical Skills](Currently working with) \
\begin{itemize}
\itemsep0em
\item Programming Languages:  Python
\item Scripting Languages: Shell
\item Tools:  PyTorch, Keras, Conda.
\item IDEs: JuPyter,  IntellijIDEA, PyCharm
\end{itemize}


\item [Technical Skills] (Past) \
\begin{itemize}
\itemsep0em
\item Programming Languages:  C, Java, C\#, Scala.
\item Scripting Languages: JavaScript, Perl.
\item Tools: DyNet, SBT, PyCharm, Matlab, Docker, Singularity, Metasploit, Meterpreter, Mutillidae, Snort, Mimikatz, Nessus, Fierce, Cewl, Nmap, JohnTheRipper, PGP, Wireshark, Nginx, Google Web Toolkit, XML, AJAX, XSLT, SOAP, CSS, WPF, WCF, ASP.Net,GDB, FUSE, Visual Source Safe, TFS, SVN, JIRA, RedMine, Telerik, Red gate, LINQ, IIS, Latex, Apache, Visual Studio, Screen, TMux, Atom, Expect, Eclipse.
\item Database: Oracle, MS SQL Server, PL SQL.\\
\end{itemize}
\item [References]  \
\begin{itemize}
\itemsep0em
\item Dr. Mihai Surdeanu (msurdeanu@email.arizona.edu), Associate Professor, Department of Computer Science, University of Arizona.
\item Dr. Rebecca Sharp (bsharp@email.arizona.edu), Assistant Professor, Department of Linguistics, University of Arizona.
\end{itemize}

\end{description}

\end{document}






