\def\pilot{{\tt PILOT}}
\def\RR{{\tt SAIL}}
\def\bb{\noindent\hspace{.46cm}$\bullet$\hspace{.19cm}}


\UseRawInputEncoding

\documentclass[10pt]{article}

%\usepackage{simplemargins}
%\setallmargins{1in}

\usepackage{url}
\evensidemargin -.2cm
\oddsidemargin -.2cm
\setlength\topmargin{-0.7in}
\setlength{\textwidth}{16cm}   % width of body
\setlength{\textheight}{9.2in}   % heigth of body
%\setlength{\sectionskip}{2ex}
\setlength{\itemsep}{-1in}
\setlength{\leftmarginii}{.05in}

\newcommand{\ve}[1]{{\em #1}} % venue of publication
\newcommand{\ti}[1]{``#1''} % title of publication
\newcommand{\lmt}{(limited to period starting 01/2013)}

\begin{document}


%\pagestyle{empty}

\begin{center}
{\Large \bf CURRICULUM VITAE\\
\bigskip{\large \bf Mithun Paul Panenghat }}
\end{center}
\smallskip

  \makebox{
     \parbox{2.6in}{\centering
     {\small
     Department of Computer Science\\
     University of Arizona\\
     Tucson, AZ 85721\\
}
     }
   \nolinebreak
     \parbox{3.2in}{\centering
	{\small Web page: \url{www2.cs.arizona.edu/people/mithunpaul/} \\
     Email: mithunpaul@email.arizona.edu\\
     Phone: (520) 395 5778	}
  }}
\bigskip

\begin{description}

\item [Education]\

\begin{tabular}{lp{4.5in}}
\hspace{-.2cm}2015 -- Present &  Ph.D.~Computer Science, {\sc University of Arizona}
\\\vspace{.0cm}&Thesis: Knowledge Distillation as a possible folution for domain transfer. 
\\\vspace{.1cm}& Adviser: Mihai~Surdeanu\\
\vspace{.1cm}\hspace{-.2cm}2014 &  M.S.~Computer Science, {\sc University of Arizona, Tucson, USA} \\
\vspace{.1cm}\hspace{-.2cm}2005 &  M.S.~Physics, {\sc Birla Institute of Technology and Science (BITS), Pilani, India} \\
\hspace{-.2cm}2005 & B.S.~Chemical Engineering,  {\sc Birla Institute of Technology and Science (BITS), Pilani, India}
\end{tabular}


\item [Professional Experience]\

\begin{tabular}{lp{4.9in}}


\hspace{-.2cm}2014 -- 2015 & Software Engineer\\\vspace{.1cm}
& {\sc Intel Corporation} \\

\hspace{-.2cm}2013 -- 2013 & Summer Intern\\\vspace{.1cm}
& {\sc The Goldman Sachs Group, Inc.} \\

\hspace{-.2cm}2011 -- 2012 & Technology Lead\\\vspace{.1cm}
&  {\sc Infosys Labs, India} \\

\hspace{-.2cm}2008 -- 2011 & Technology Associate\\\vspace{.1cm}
& {\sc Infosys Labs, India} \\

\hspace{-.2cm}2005 -- 2008 & Software Engineer	\\
& {\sc Infosys Ltd, India} 

\end{tabular}

\vspace{-.3cm}
\item [Honors, Awards, and Memberships]\

Finalist, three minute thesis competition, University of Arizona, March 2018\\
Member of the team that ranked 4th at the Fake News Challenge shared task, 2017\\
Member of the honor society Phi Kappa Phi, 2012 -- 2014\\
Best research paper award, International Conference on Services in Emerging Markets, 2011\\
Most valuable player,  Infosys  Ltd., 2008\\
Member of the team that ranked 2nd at a national trivia challenge and invited for a dinner with the President of India, 2005\\
Junior Research Fellow, Indian Institute of Science, Bangalore (2001 – 2003)\\




\vspace{-.4cm}\item [Conference Reviews]\ 

Fact Extraction and Verification (FEVER) workshop, Empirical Methods in Natural Language Processing (EMNLP), 2018\\
Fact Extraction and Verification (FEVER) workshop, Empirical Methods in Natural Language Processing (EMNLP), 2019\\
Language Resources and Evaluation Conference (LREC), 2020\\







\item [Competitive Peer-Reviewed Conference Publications]\


(* denotes equal contributions from the authors)

\begin{enumerate}

\item Sandeep Suntwal*, Mithun Paul*, Rebecca Sharp, and Mihai Surdeanu.   \ti{On the Importance of Delexicalization for Fact Verification}. In \ve{ the Proceedings of the Empirical Methods in Natural Language Processing (EMNLP)}, 2019.

\item  Rebecca Sharp et al,   \ti{Eidos \& Delphi: From Free Text to Executable Causal Models}. In \ve{ the Proceedings Annual Conference of the North American Chapter of the Association for Computational Linguistics (NAACL-HLT)}, 2019.

\end{enumerate}

\item [Less Competitive Peer-Reviewed Conference and Workshop Publications]\

\begin{enumerate}
\setcounter{enumi}{2}


\item Sandeep Suntwal*, Mithun Paul*, Rebecca Sharp, and Mihai Surdeanu.   \ti{On the Importance of Delexicalization for Fact Verification}. In \ve{Proceedings of the BlackboxNLP Workshop}, 2019.

\item Mithun Paul, Rebecca Sharp and Mihai Surdeanu,.   \ti{A mostly unlexicalized model for recognizing textual entailment}. In \ve{Proceedings of the Fact Verification workshop}, 2018.

\item Rebecca Sharp, Mithun Paul, Ajay Nagesh, Dane  Bell, and Mihai Surdeanu.   \ti{Grounding Gradable Adjectives through Crowdsourcing}. In \ve{Proceedings of the eleventh edition of the Language Resources and Evaluation Conference (LREC)}, 2018.

\item Mithun Paul, Derek Bambauer and Christian Collberg.   \ti{A Possible Solution For Privacy Preserving Cloud Data Storage}. In \ve{Proceedings of IEEE International Conference on Cloud Computing}, 2015.

\item  Mithun Paul, Nitin Singh Chauhan and Ashutosh Saxena.   \ti{A Security Analysis of Smartphone Data Flow and feasible solutions for lawful interception}. In \ve{ Proceedings for the IEEE 7th International Conference on Information Assurance and Security}, 2011.

\item  Mithun Paul, M. Choudary Gorantla and Ashutosh Saxena.   \ti{Group Key Exchange with Non Linear Trust}. In \ve{ Proceedings for The IEEE Fifth International Conference on Internet Multimedia Systems Architecture and Applications}, 2011.

\item  Mithun Paul and Ashutosh Saxena.   \ti{Data Shredding Service For Cloud}, In \ve{  Proceedings of the 2nd International Conference on Services in Emerging Markets}. 2011.

\item  Mithun Paul and Ashutosh Saxena.   \ti{Proof Of Erasability For Ensuring Comprehensive Data Deletion In Cloud Computing}. In \ve{  Proceedings of the Third International Conference, Communications in Computer and Information Science}, 2010.

\item  Mithun Paul and Ashutosh Saxena.   \ti{Zero Data Remnance Proof in cloud Storage}. In \ve{  International Journal of Network Security \& Its Applications (IJNSA), Vol.2, No.4}, 2010.




\end{enumerate}


\item [Work in Progress] \
\begin{enumerate}
\setcounter{enumi}{11}

\item Mithun Paul Panenghat, Sandeep Suntwal, Faiz Rafique, Rebecca Sharp, and Mihai Surdeanu.   \ti{Towards the Necessity for Debiasing Natural Language Inference Datasets}. submitted to \ve{the Language Resources and Evaluation Conference (LREC)}, 2020.

\item Mithun Paul Panenghat, Sandeep Suntwal, Faiz Rafique, Rebecca Sharp, and Mihai Surdeanu.   \ti{A Student Teacher Architecture for Learning Semantic Lifting}.To be submitted to \ve {the Empirical Methods in Natural Language Processing (EMNLP)}, 2020.

\end{enumerate}


\item [Patents] \
\begin{enumerate}
%\setcounter{enumi}{63}

\item 
Ashutosh Saxena, Vishal Krishna Saxena, Kaushal Saxena, Kumar Surni, Mithun Paul. \ti{Method and System for Providing Masking Services}.  US patent No. US8881224B2.
\item 
Ashutosh Saxena, Mithun Paul. \ti{System and method for deletion of data in a remote computing platform}.  US patent No. US8504532B2.
\item 
Sravan R, Mithun Paul, Ashutosh Saxena. \ti{Methods for dynamic destruction of data in a remote data storage platform and devices thereof}.  US patent No. US9740726B2.


\end{enumerate}




\item [Colloquium Presentations]\

\begin{enumerate}

\item School of Information colloquia, University of Arizona, Nov 2019
\item Department of Computer Science colloquia, University of Arizona, Sep 2019
\item March for Science, AZ, Tucson , Arizona, Feb 2019
\item Three minute thesis competition, University of Arizona, March 2018

\end{enumerate}



\newpage
\vspace{-.1cm}\item [List of Collaborators ](excluding advisor Mihai Surdeanu) \

\begin{center}
 \begin{tabular}{l|l|l|l}
 {\bf Last Name} & {\bf First Name} & {\bf Relation} & {\bf Current Institution} \\
 \hline
Bachman & John & Co-author & Harvard Medical School \\
Bambauer &Derek  & Co-author & University of Arizona \\
Barnard & Kobus & Co-author & University of Arizona \\
Bell & Dane & Co-author & University of California at Davis \\
Bethard & Steve & Co-author & University of Arizona \\
Collberg & Christian & Co-author & University of Arizona \\
Gyori & Benjami & Co-author & Harvard Medical School \\
Luo & Fan & Co-author & University of Arizona \\
Morrison & Clayton & Co-author & University of Arizona \\
Nagesh & Ajay & Co-author & University of Arizona \\
Pyarelal & Adarsh & Co-author & University of Arizona \\
Saxena & Kaushal & Co-author & Crunchbase \\
Saxena & Ashutosh & Co-author & CMR University \\
Sharp & Rebecca & Co-author & University of Arizona \\
Tang & Zheng & Co-author & University of Arizona \\
Valenzuela-Escarcega & Marco & Co-author & University of Arizona \\
Yadav & Vikas & Co-author & University of Arizona \\


\end{tabular}
\end{center}


\end{description}

\end{document}




