\def\pilot{{\tt PILOT}}
\def\RR{{\tt SAIL}}
\def\bb{\noindent\hspace{.46cm}$\bullet$\hspace{.19cm}}


\UseRawInputEncoding

\documentclass[10pt]{article}

%\usepackage{simplemargins}
%\setallmargins{1in}

\usepackage{url}
\evensidemargin -.2cm
\oddsidemargin -.2cm
\setlength\topmargin{-0.7in}
\setlength{\textwidth}{16cm}   % width of body
\setlength{\textheight}{9.2in}   % heigth of body
%\setlength{\sectionskip}{2ex}
\setlength{\itemsep}{-1in}
\setlength{\leftmarginii}{.05in}

\newcommand{\ve}[1]{{\em #1}} % venue of publication
\newcommand{\ti}[1]{``#1''} % title of publication
\newcommand{\lmt}{(limited to period starting 01/2013)}

\begin{document}


%\pagestyle{empty}

\begin{center}
{\Large \bf CURRICULUM VITAE\\
\bigskip{\large \bf Mithun Paul Panenghat }}
\end{center}
\smallskip

  \makebox{
     \parbox{2.6in}{\centering
     {\small
     Department of Computer Science\\
     University of Arizona\\
     Tucson, AZ 85721\\
}
     }
   \nolinebreak
     \parbox{3.2in}{\centering
	{\small Web page: \url{www2.cs.arizona.edu/people/mithunpaul/} \\
     Email: mithunpaul@email.arizona.edu\\
     Phone: (520) 395 5778	}
  }}
\bigskip

\begin{description}

\item [Education]\

\begin{tabular}{lp{4.5in}}
\hspace{-.2cm}2015 -- Present &  Ph.D.~Computer Science, {\sc University of Arizona}
\\\vspace{.0cm}&Thesis: 
\\\vspace{.1cm}& Adviser: Mihai~Surdeanu\\
\vspace{.1cm}\hspace{-.2cm}2014 &  M.S.~Computer Science, {\sc University of Arizona, Tucson, USA} \\
\vspace{.1cm}\hspace{-.2cm}2005 &  M.S.~Physics, {\sc Birla Institute of Technology and Science (BITS), Pilani, India} \\
\hspace{-.2cm}2005 & B.S.~Chemical Engineering,  {\sc Birla Institute of Technology and Science (BITS), Pilani, India}
\end{tabular}


\item [Professional Experience]\

\begin{tabular}{lp{4.9in}}


\hspace{-.2cm}2014 -- 2015 & Software Engineer\\\vspace{.1cm}
& {\sc Intel Corporation} \\

\hspace{-.2cm}2013 -- 2013 & Summer Intern\\\vspace{.1cm}
& {\sc The Goldman Sachs Group, Inc.} \\

\hspace{-.2cm}2011 -- 2012 & Technology Lead\\\vspace{.1cm}
&  {\sc Infosys Labs, India} \\

\hspace{-.2cm}2008 -- 2011 & Technology Associate\\\vspace{.1cm}
& {\sc Infosys Labs, India} \\

\hspace{-.2cm}2005 -- 2008 & Software Engineer	\\
& {\sc Infosys Ltd, India} 

\end{tabular}

\vspace{-.3cm}
\item [Honors, Awards, and Memberships]\

Finalist, three minute thesis competition, University of Arizona, March 2018\\
Member of the team that ranked 4th at the Fake News Challenge shared task, 2017\\
Member of the honor society Phi Kappa Phi, 2012 -- 2014\\
Best research paper award, International Conference on Services in Emerging Markets, 2011\\
Most valuable player,  Infosys  Ltd., 2008\\
Member of the team that ranked 2nd at a national trivia challenge and invited for a dinner with the President of India, 2005\\
Junior Research Fellow, Indian Institute of Science, Bangalore (2001 – 2003)\\




\vspace{-.4cm}\item [Conference Reviews]\ 

Fact Extraction and Verification (FEVER) workshop, Empirical Methods in Natural Language Processing (EMNLP), 2018\\
Fact Extraction and Verification (FEVER) workshop, Empirical Methods in Natural Language Processing (EMNLP), 2019\\
Language Resources and Evaluation Conference (LREC), 2020\\







\item [Competitive Peer-Reviewed Conference Publications]\


(* denotes equal contributions from the authors)

\begin{enumerate}

\item Sandeep Suntwal*, Mithun Paul*, Rebecca Sharp, and Mihai Surdeanu.   \ti{On the Importance of Delexicalization for Fact Verification}. In \ve{ the Proceedings of the Empirical Methods in Natural Language Processing (EMNLP)}, 2019.

\item  Rebecca Sharp et al,   \ti{Eidos \& Delphi: From Free Text to Executable Causal Models}. In \ve{ the Proceedings Annual Conference of the North American Chapter of the Association for Computational Linguistics (NAACL-HLT)}, 2019.

\end{enumerate}

\item [Less Competitive Peer-Reviewed Conference and Workshop Publications]\

\begin{enumerate}
\setcounter{enumi}{2}


\item Sandeep Suntwal*, Mithun Paul*, Rebecca Sharp, and Mihai Surdeanu.   \ti{On the Importance of Delexicalization for Fact Verification}. In \ve{Proceedings of the BlackboxNLP Workshop}, 2019.

\item Mithun Paul, Rebecca Sharp and Mihai Surdeanu,.   \ti{A mostly unlexicalized model for recognizing textual entailment}. In \ve{Proceedings of the Fact Verification workshop}, 2018.

\item Rebecca Sharp, Mithun Paul, Ajay Nagesh, Dane  Bell, and Mihai Surdeanu.   \ti{Grounding Gradable Adjectives through Crowdsourcing}. In \ve{Proceedings of the eleventh edition of the Language Resources and Evaluation Conference (LREC)}, 2018.

\item Mithun Paul, Derek Bambauer and Christian Collberg.   \ti{A Possible Solution For Privacy Preserving Cloud Data Storage}. In \ve{Proceedings of IEEE International Conference on Cloud Computing}, 2015.

\item  Mithun Paul, Nitin Singh Chauhan and Ashutosh Saxena.   \ti{A Security Analysis of Smartphone Data Flow and feasible solutions for lawful interception}. In \ve{ Proceedings for the IEEE 7th International Conference on Information Assurance and Security}, 2011.

\item  Mithun Paul, M. Choudary Gorantla and Ashutosh Saxena.   \ti{Group Key Exchange with Non Linear Trust}. In \ve{ Proceedings for The IEEE Fifth International Conference on Internet Multimedia Systems Architecture and Applications}, 2011.

\item  Mithun Paul and Ashutosh Saxena.   \ti{Data Shredding Service For Cloud}, In \ve{  Proceedings of the 2nd International Conference on Services in Emerging Markets}. 2011.

\item  Mithun Paul and Ashutosh Saxena.   \ti{Proof Of Erasability For Ensuring Comprehensive Data Deletion In Cloud Computing}. In \ve{  Proceedings of the Third International Conference, Communications in Computer and Information Science}, 2010.

\item  Mithun Paul and Ashutosh Saxena.   \ti{Zero Data Remnance Proof in cloud Storage}. In \ve{  International Journal of Network Security \& Its Applications (IJNSA), Vol.2, No.4}, 2010.




\end{enumerate}


\item [Work in Progress] \
\begin{enumerate}
\setcounter{enumi}{11}

\item Mithun Paul Panenghat, Sandeep Suntwal, Faiz Rafique, Rebecca Sharp, and Mihai Surdeanu.   \ti{Towards the Necessity for Debiasing Natural Language Inference Datasets}. submitted to \ve{the Language Resources and Evaluation Conference (LREC)}, 2020.

\item Mithun Paul Panenghat, Sandeep Suntwal, Faiz Rafique, Rebecca Sharp, and Mihai Surdeanu.   \ti{A Student Teacher Architecture for Learning Semantic Lifting}.To be submitted to \ve {the Empirical Methods in Natural Language Processing (EMNLP)}, 2020.

\end{enumerate}


\item [Patents] \
\begin{enumerate}
%\setcounter{enumi}{63}

\item 
Ashutosh Saxena, Vishal Krishna Saxena, Kaushal Saxena, Kumar Surni, Mithun Paul. \ti{Method and System for Providing Masking Services}.  US patent No. US8881224B2.
\item 
Ashutosh Saxena, Mithun Paul. \ti{System and method for deletion of data in a remote computing platform}.  US patent No. US8504532B2.
\item 
Sravan R, Mithun Paul, Ashutosh Saxena. \ti{Methods for dynamic destruction of data in a remote data storage platform and devices thereof}.  US patent No. US9740726B2.


\end{enumerate}


\item [Invited Scholarly Presentations] \lmt \
\begin{enumerate}

\item Keynote at the Intl. Conf. on Natural Language and Information Systems (NLDB), june 2107
\item Bill and Melinda Gates Foundation, February 2017
\item Harvard Medical School, Harvard University, November 2016
\item Bill and Melinda Gates Foundation, October 2016
\item Technical University of Cluj-Napoca, May 2016
\item Paul Allen Institute for Artificial Intelligence, October 2013
\end{enumerate}

\item [Conference Presentations] \lmt \

(\& indicates talks/posters co-presented with students, postdocs, or collaborators. \% indicates talks/posters presented solely by students, postdocs, or collaborators)


\begin{enumerate}

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
International Conference on Computational Linguistics (COLING), 2016

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Empirical Methods in Natural Language Processing (EMNLP), 2016

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Workshop on Biomedical Natural Language Processing (BioNLP), 2016

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Language Resources and Evaluation Conference (LREC), 2016

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Annual meeting of the Association for Computational Linguistics (ACL), 2015

\item 
[\& \addtocounter{enumi}{1}\theenumi ]
North American Chapter of the Association for Computational Linguistics - Human Language Technologies (NAACL HLT), 2015

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Third Joint Conference on Lexical and Computational Semantics (*SEM), 2014

\item 
[\& \addtocounter{enumi}{1}\theenumi ]
Annual Meeting of the Association for Computational Linguistics (ACL), 2014

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Language Resources and Evaluation Conference (LREC), 2014

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
Congreso de la Sociedad Espa\~{n}ola para el Procesamiento del Lenguaje Natural (SEPLN), 2014

\item 
International Conference on Artificial Intelligence and Law (ICAIL), 2013

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
IEEE Workshop on Interactive Visual Text Analytics, 2013

\item 
[\% \addtocounter{enumi}{1}\theenumi ]
NIST TAC-KBP 2013 Workshop, 2014

\item 
NIST TAC-KBP 2013 Workshop, 2013


\end{enumerate}


\item [Colloquium Presentations]\

\begin{enumerate}
\item UA College of ScienceÕs Science Cafe, Fall 2016
\item UA Honors College Smart Talk, Spring 2015
\item UA Linguistics colloquium, Fall 2014
\item UA Cognitive Science colloquium, Fall 2014
\item UA Computer Science colloquium, Spring 2013
\item UA Linguistics colloquium, Spring 2013
\end{enumerate}

\item [Open-Source Software]\

\begin{enumerate}

\item REACH: biomedical information extraction suite
\begin{itemize}
\item \url{https://github.com/clulab/reach}
\item Top performer in the machine reading evaluation organized by the DARPA Big Mechanism program
\end{itemize}

\item Processors: NLP suite in Scala
\begin{itemize}
\item \url{https://github.com/clulab/processors }
\end{itemize}

\item CoreNLP: Stanford NLP software suite
\begin{itemize}
\item \url{https://stanfordnlp.github.io/CoreNLP/}
\item Downloads in the tens of thousands
\end{itemize}

\item Multi-instance multi-label relation extraction
\begin{itemize}
\item \url{https://nlp.stanford.edu/software/mimlre.shtml}
\end{itemize}

\item SBEP: Stanford Biomedical Event Parser 
\begin{itemize}
\item \url{https://nlp.stanford.edu/software/eventparser.shtml}
\end{itemize}

\item Ensemble: Linearly-interpolated Dependency Parsers
\begin{itemize}
\item \url{http://www.surdeanu.info/mihai/ensemble/ }
\end{itemize}

\item Swirl: the Semantic Role Labeler
\begin{itemize}
\item \url{http://www.surdeanu.info/mihai/swirl/}
\end{itemize}

\item Bios: Suite of Syntactico-Semantic Analyzers
\begin{itemize}
\item \url{http://www.surdeanu.info/mihai/bios/ }
\end{itemize}

\item Spear: Syntactic Parser
\begin{itemize}
\item \url{http://www.surdeanu.info/mihai/spear/ }
\end{itemize}

\end{enumerate}


\item [Grants]\
\begin{enumerate}

\item \ti{An Exploratory System for Complex World Modeling}, \ve{DARPA} -- subcontract from the Florida Institute for Human and Machine Cognition (IHMC). Sole PI at UA. \$149K, 2017 -- 18, 8\% effort

\item \ti{Development of Causal Models with the Aid of Natural Language Processing (NLP) Technology}, \ve{Bill and Melinda Gates Foundation}. Sole PI. \$313K, 2016 -- 17, 16\% effort

\item \ti{Large-scale Non-invasive Detection of Type 2 Diabetes Risk through Machine Learning and Visualization on Social Media}, \ve{Accelerate for Success Program, University of Arizona}. PI, other co-PIs: Stephen Kobourov, Melanie Hingle, and Stephen Rains. \$97K, 2017

\item \ti{REACH: Reading and Assembling Contextual and Holistic Mechanisms from Text}, \ve{DARPA}. PI, other co-PIs: Kobus Barnard, Clayton Morrison, Angus Forbes, Ryan Gutenkunst, and Guang Yao. \$3.6M, 2014 -- 2017, 19\% effort

\item \ti{Enhancing Nurse Decision-Making via Augmented Communication Tools (ACTs)}, \ve{NIH}. PI: Jane Carrington, co-PIs: Mihai Surdeanu, Angus Forbes. \$745K, 2014 -- 2017, 8\% effort

\item \ti{Robust Approximate Inference for Question Answering}, \ve{Allen Institute for Artificial Intelligence}. Sole PI. \$149K, 2013 -- 2015, 10\% effort

\item \ti{Question Answering Using Linguistics Features and Discourse Modeling}, \ve{Allen Institute for Artificial Intelligence}. Sole PI. \$90K, 2013, 16\% effort

\end{enumerate}

\vspace{-.1cm}\item [Courses Developed, Revised, and Taught]\
	
Text Retrieval and Web Search (developed and taught at UA)\\
Applied Natural Language Processing  (developed and taught at UA)\\
Statistical Foundations for the Information Age (revised and taught at UA)\\
Advanced Topics in Computational Intelligence Seminar (developed and taught at UA)

\vspace{-.1cm}\item [Postdoc~Advisees]\

Ajay Nagesh, 2017 -- present\\
March Valenzuela, 2016 -- present\\
Peter Jansen, 2013 -- 2015, currently tenure-track faculty in the School of Information at UA

\vspace{-.1cm}\item [Ph.D.~(Co)Advisees]\

Mithun Paul, CS, 1st year \\
Joshua Meyer, Linguistics, co-advised with T. Beaver, expected graduation Summer 2018 \\
Dane Bell, Linguistics, co-advised with A. Wedel, expected graduation Spring 2018 \\
Gustave Hahn-Powell, Linguistics, co-advised with S. Fong, expected graduation Spring 2018 \\
Rebecca Sharp, Linguistics, co-advised with M. Hammond, expected graduation Summer 2017 \\
Marco Valenzuela, CS, graduated Spring 2016 \\
Heeyoung Lee, Stanford Linguistics, co-advised with D. Jurafsky, graduated Spring 2016 \\
Anh Tran, CS, co-advised with P. Cohen, graduated Summer 2014

\vspace{-.1cm}\item [M.S.~Thesis (Co)Supervision ]\
%(12 refereed publications with MS co-authors)]\

Benjamin Gaska, CS, co-advised with M. Strout, expected graduation Spring 2017\\
Rebecca Sharp, Linguistics, graduated Spring 2014 \\
Gustave Hahn-Powell, Linguistics, graduated Spring 2014 

\vspace{-.1cm}\item [Honors Thesis Supervision ]\

Katherine Fackrell, SISTA, Spring 2015 \\
Daniel Fried, CS/SISTA, Spring 2014

\vspace{-.1cm}\item [Service on PhD Dissertation Committees other than Advisor ]\

Glen Pink, CS University of Sydney, expected graduation Spring 2017 \\
Yekaterina Kharitonova, CS, graduated Spring 2016 \\
Jeremy Wright, CS, graduated Spring 2015 

\newpage
\vspace{-.1cm}\item [List of Collaborators ] (excluding advisees, past 5 years)\

\begin{center}
 \begin{tabular}{l|l|l|l}
 {\bf Last Name} & {\bf First Name} & {\bf Relation} & {\bf Current Institution} \\
 \hline
Agirre & Eneko & Co-author & University of Basque Country \\
%\hline
Balasubramanian & Niranjan & Co-author & Stony Brook University \\
Barnard & Kobus & Co-author & University of Arizona \\
Bauer & John & Co-author & Stanford University \\
Bethard & Steven & Co-author & University of Arizona \\
Carrington & Jane & Co-author & University of Arizona \\
Chambers & Nate & Co-author & US Naval Academy \\
Chang & Angel & Co-author & Google \\
Clark & Peter & Co-author & Allen Institute for AI \\
Cohen & Paul & Co-author & DARPA/University of Arizona \\
Dawson & Colin & Co-author & Oberlin College \\
De Lacalle & Oier Lopez & Co-author & University of Basque Country \\
Del Pero & Luca & Co-author & University of Arizona \\
Finkel & Jenny & Co-author & Prismatic \\
Forbes & Angus & Co-author & University of Illinois \\
Hammond & Mike & Co-author & University of Arizona \\
Hicks & Thomas & Co-author & University of Arizona \\
Hingle & Melanie & Co-author & University of Arizona \\
Intxaurrondo & Ander & Co-author & University of Basque Country \\
Jankowiak & Martin & Co-author & Stanford University \\
Jansen & Peter & Co-author & University of Arizona \\
Jeruss & Sara & Co-author & Facebook \\
Ji & Heng & Co-author & Rensselaer Polytechnic Institute \\
Johansson & Richard & Co-author & University of Gothenburg \\
Jurafsky & Dan & Co-author & Stanford University \\
Kobourov & Stephen & Co-author & University of Arizona \\
MacCartney & Bill & Co-author & Google \\
Manning & Christopher & Co-author & Stanford University \\
McCallum & Andrew & Co-author & University of Massachusetts  \\
McClosky & David & Co-author & Google  \\
Morrison & Clayton & Co-author &  University of Arizona \\
Nallapati & Ramesh & Co-author & IBM \\
Peirsman &  Yves & Co-author & University of Leuven \\
Recasens & Marta & Co-author & Google \\
Reschke & Kevin & Co-author & Stanford University \\
Riedel & Sebastian & Co-author & University College London \\
Tibshirani & Julie & Co-author & Stanford University \\
Zapirain & Benat & Co-author & University of Basque Country \\


\end{tabular}
\end{center}


\end{description}

\end{document}




